Stability of variational quantum dynamics with Gaussian approximants

### 2013-10-03 paper.tex
Started new dual paper

The projector satisfies
$$π^{-1}\int |α〉〈α|\,d²α=1.$$
This is similar to the law for an orthonormal basis, except that the left hand side must be scaled by $π$.  Therefore, any state can be expanded as a sum over coherent states, in the form
$$|ψ〉=π^{-1}\int |α〉〈α|ψ〉\,d²α.\tag\csproj$$
However, this expansion is not unique: a coherent state $|β〉$ has the trivial expansion $|β〉=|α〉$, but the expansion given by Equations~\csproj\ and~\csip\ is a gaussian function of $α$.  A set of states like this is known as a frame, in distinction from a basis, whose elements are linearly independent, and whose expansions are unique.  Further properties of the coherent states will be stated as required.  Glauber's summary of them\cite{prx-131-2766} is paraphrased in every quantum optics textbook ever written.

>>>>

The projector satisfies
$$\int |α〉〈α|\,d²α=π.$$
If the right hand side were 1, this would indicate that the coherent states were an orthonormal basis of ket space.  As it is, any state can be expanded as a combination of coherent states, in the form
$$|ψ〉=π^{-1}\int |α〉〈α|ψ〉\,d²α.\tag\csproj$$
However, this expansion is not unique: a coherent state $|β〉$ has the trivial expansion $|β〉=|α〉$, but the expansion given by Equations~\csproj\ and~\csip\ is a gaussian function of $α$.  A set of states like this is known as a frame, in distinction from a basis, whose elements are linearly independent, and whose expansions are unique.  Sets such as the coherent states are known as a Gabor frame.  Further properties of the coherent states will be stated as required.  Glauber's summary of them\cite{prx-131-2766} is paraphrased in every quantum optics textbook ever written.
